---
title: "Day 4 Interactive"
format: html
editor: visual
---

## Functions

Make a function that doubles a value.

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(my_dollars = 10.13)
```

```{r}
double_value(10.13)
```

```{r}
double_value(my_dollars = 10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees fahrenheit, write a function that converts it to Celsius.

```{r}
convert_f_to_c <- function(temp_f) {
  print((temp_f - 32) * (5 / 9))
}
```

```{r}
convert_f_to_c(temp_f = 52)
```

Create a function that given inputs of age and hometown, returns "I am \_\_\_ years old, and I'm from \_\_\_\_\_"

```{r}
about_me <- function(age_yr, hometown) {
  print(paste0("I am ", age_yr, " years old, and I'm from ", hometown, "."))
}

about_me(age_yr = 6, hometown = "Los Angeles")
```

```{r}
double_value2 <- function(dollars) {
  dollars * 2
}
```

```{r}
tax2023 <- double_value2(dollars = 10) * 0.08
```

```{r}

```

Print statements and return statements

Print: "show me", Return: "store this so I can use it later"

## Functions with conditionals

```{r}
calculate_animal_age <- function(species, age_human_years) {
  if (species == "dog") {
    age_human_years * 7
  } else if (species == "goat") {
    age_human_years * 4.7
  } else {
    print("Please enter dog or goat.")
  }
}
```

```{r}
calculate_animal_age(species = "dog", age_human_years = 10)

calculate_animal_age(species = "goat", age_human_years = 4)

calculate_animal_age(species = "whale", age_human_years = 10)
```

Write a function that, given temperature in Kelvin, if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit.

```{r}
convert_kelvin <- function(scale, temp_k) {
  if (scale == "metric") {
    print(temp_k - 273.15)
  } else if (scale == "english") {
    print(((temp_k - 273.15) * 1.8) + 32)
  }
}
```

```{r}
my_value = convert_kelvin(scale = "metric", temp_k = 40)
```
